---
title: "initial_viz"
author: "Matthew Ross"
date: "10/14/2019"
output: html_document
---

```{r setup, include=FALSE}
library(raster)
library(tidyverse)
library(dygraphs)
library(sf)
library(nhdplusTools)
library(mapview)
library(elevatr)
library(xml2)
library(rvest)
library(lubridate)
library(imputeTS)
library(ggthemes)
```


# Just time series

```{r}
files <- list.files('data/oct', full.names = T)
files <- list.files("/Users/natalieschmer/Desktop/GitHub/sensors/Data/Nov17/nov17sensor/", full.names = T)

better_names <- tibble(
  og_names = c(
    'Date Time',
    'DO (mg/L)',
    '% sat',
    'ORP (mV)',
    'Specific Conductivity (µS/cm)',
    'Temperature (C)',
    'pH (pH)',
    'Turbidity (NTU)',
    'Depth (ft)'
  ),
  better_names = c(
    'datetime',
    'do_mg',
    'dissolved oxygen',
    'orp',
    'salinity',
    'temp',
    'ph',
    'turb',
    'depth'
  )
)
weird_html_reader <- function(file) {
  raw_wrong <- read_html(file) %>%
    html_node('table') %>%
    html_table(., fill = T) %>%
    slice(-1:-7)
  
  names <- raw_wrong %>%
    slice(1) %>%
    gather(key = 'key', value = 'og_names') %>%
    mutate(og_names = ifelse(grepl('sat', og_names), '% sat', og_names)) %>%
    left_join(better_names) %>%
    select(-key)
  
  names(raw_wrong) <- names$better_names
  
  raw_right <- raw_wrong %>%
    slice(-1) %>%
    mutate_at(vars(-`datetime`), as.numeric) %>%
    mutate(datetime = ymd_hms(datetime)) %>%
    mutate(site=str_split_fixed(file,'_',3)[,2])
}    

sensors <- map_dfr(files,weird_html_reader)

rist_dist <- c(8.5,15,16.2,18.5,19.9)

```




```{r}
full_seq <- tibble(datetime= seq(min(sensors$datetime),
                                 max(sensors$datetime),by=15*60))  %>%
  nest(data = everything())




full_unfold <- tibble(site=unique(sensors$site),
                    full_time = rep(full_seq$data,length(site))) %>%
  unnest(full_time)

sensors_clean <- sensors %>%
  mutate(depth_lead = lead(depth_ft,1),
         depth_rate = depth_ft-depth_lead) %>%
  filter(depth_ft > 0 & depth_ft < 10,
         temp_c > 0) %>%
  right_join(.,full_unfold,by=c('datetime','site')) %>%
  gather(key='sensor',value='value',-site,-datetime) 

s# %>%
#   group_by(sensor,site) %>%
#   mutate(fill_value = na_interpolation(value,'linear')) %>%
#   mutate(fill_filter = 
#            signal::filter(signal::butter(2,1/5,type='low'),fill_value)) %>%
#   as_tibble() %>%
#   filter(day(datetime) >= 8 & day(datetime) < 13)

summary(oct_clean)
oct_depth <- oct_clean %>%
  select(-value,-fill_value) %>%
  spread(key='sensor',value='fill_filter') %>%
  select(datetime,salinity,site) %>%
  spread(key='site',value='salinity')

dygraph(xts::xts(oct_depth %>% select(-datetime),order.by=oct_depth$datetime))
```



```{r}
velocity <- 0.52*.3048*60 # m/minute

rist_time <- c(0,(rist_dist*1000)/(velocity)/60) # Hours

unique(oct_clean$site)

site_time = tibble(site = c('Rist',
                            'Legacy',
                            'Timberline',
                            'Prospect',
                            'ELC',
                            'Archery'),
                   time = rist_time)


oct_hour <- oct_clean %>%
  mutate(hour = round_date(datetime,'hours')) %>%
  group_by(hour,site,sensor) %>%
  summarize(value = mean(fill_filter,na.rm=T))

oct_hour_sc <- oct_clean %>%
  inner_join(site_time) %>%
  filter(sensor %in% c('depth','salinity','dissolved oxygen')) %>%
  mutate(sensor = factor(sensor,levels=c('depth','salinity','dissolved oxygen'))) %>%
  mutate(site = factor(site,levels=c('Rist','Legacy',
                                     'Timberline','Prospect',
                                     'ELC','Archery'))) %>%
  mutate(jumptime = datetime+time*60*60) %>%
  group_by(site,sensor) %>%
  mutate(ristCounter = c(0,diff(datetime)) %>% cumsum(.)/60) %>%
  filter(ristCounter >= time)





times <- unique(oct_hour_sc$datetime) %>% sort()

iseq = seq(1,length(times),by=1)

times
saveGIF({
  for(i in iseq){
    dat <- oct_hour_sc %>%
      filter(datetime <= times[i])
    precise_dat <- oct_hour_sc %>%
      filter(datetime <= times[i]) %>%
      arrange(desc(datetime)) %>%
      group_by(site,sensor) %>%
      slice(1)
g1 <- ggplot(oct_hour_sc,aes(x=datetime,y=fill_value,color=site)) + 
  geom_line(size=.1) + 
  geom_line(size=3,color='white') +
  geom_line(data=dat,size=1.1) + 
  geom_point(data=precise_dat,size=10) + 
  xlab('Date') + 
  ylab('Sensor Recording') + 
  theme_few(base_size=30) + 
  scale_color_brewer(type='div',palette=3,direction=-1,name='') + 
  facet_wrap(~sensor,scales='free',ncol=1) + 
  theme(legend.position = 'none') + 
  xlim(min(times),max(times)) 
print(g1)
  }
},movie.name='test4.gif',interval=0.075,ani.width=1600,ani.height=900)

```


# Poudre river 

Is cool

## This guy

Made a really cool viz [here](https://statnmap.com/2019-10-06-follow-moving-particle-trajectory-on-raster-with-rayshader/) 

## I wanna 

Make the same


# The physical template

## NHD flowline downloads

Thanks David Blodgett, writer of nhdplustools

```{r}


poudre_outlet <-  st_sfc(st_point(c(-104.999820, 40.538851)), crs = 4326) 

poudre_comid <- discover_nhdplus_id(poudre_outlet)

poudre_lines <- navigate_nldi(list(featureSource = 'comid',
                               featureID = poudre_comid),
                               mode='UM',
                               data_source = '')




#Download the full set
subset_nhdplus(comids=poudre_lines$nhdplus_comid,
                              output_file = 'data/poudre.gpkg',
               nhdplus_data = 'download')


```


## Clip to lower part of the canyon

```{r}


big_box <- st_bbox(c(xmin=-105.36,
                   xmax=-104.984,
                   ymax=40.732,
                   ymin=40.522),crs=4326) %>%
  st_as_sfc()


sub_poudre <- poudre_lines[big_box,] %>%
  st_transform(2163)



sites <- st_read('data/sondes.kml') %>%
  filter(Name != 'Manners Sonde (FC-existing)') %>%
  mutate(Name = factor(Name,levels=c('Rist Canyon Rd (CSU)',
                                     'Legacy (CSU)',
                                     'Lincoln (In-situ)',
                                     'Timberline (FC)',
                                     'Prospect (FC)',
                                     'ELC (CSU; online)',
                                     'Archery Range (FC)',
                                     'Fossil Creek (FC)')))


mapview(sites,zcol='Name',col.regions=c('#1b7837','#7fbf7b','gray',
                                        '#d9f0d3','#e7d4e8',
                                        '#af8dc3','#762a83','gray'
                                        ))



subsub <- sub_poudre[sites %>% st_transform(2163) %>% st_bbox(),]

mapview(subsub)
```


## Download raster data

```{r}
p_elev <- get_elev_raster(sub_poudre,z=8)

e_sub <- crop(p_elev,(sub_poudre))

```


## Collapse poudre river to saingle flowline and sample it

```{r}
poudre_solo <- sub_poudre %>%
  summarize()


poudre_sample <- st_sample(poudre_solo$geometry,size=10,type='regular') %>%
  st_sf() 


mapview(poudre_sample)

```


## Copy amazing code

This is the core innovation I'm copying from StatnMap, basically
it reprojects an SF object into rayshader space. 

```{r}
zscale=40

poudre_rays <- sf_proj_as_ray(e_sub,sf = poudre_sample,
                              z_pos = maxValue(e_sub) + 10,
                              zscale = zscale,crop=T)



```

## Setup the terrain scene

```{r}
library(rayshader)
datamat <- t(as.matrix(e_sub))
# Rayshade raster
ambmat <- ambient_shade(datamat, zscale = zscale)
raymat <- ray_shade(datamat, zscale = zscale, lambert = TRUE)

# Create ray_image
ray_image <- datamat %>%
  sphere_shade(texture = "imhof4") %>%
  add_shadow(raymat, max_darken = 0.5) %>%
  add_shadow(ambmat, max_darken = 0.5)


```



## More copying (movie renderer)

```{r}
library(rgl)
render_cropped_scene <- function(ray_image, datamat, position,
                                 position_next,
                                 window = 200,
                                 zscale = 30, zoom = 0.4,
                                 windowsize = c(1000, 1000)) {
  # Create a window around point
  bounds <- tibble(
    Xmin = max(round(position)[1] - window, 0), # X
    Xmax = min(round(position)[1] + window, dim(datamat)[1]),
    Ymin_pos = max(round(position)[3] - window, -dim(datamat)[2]), # Y
    Ymax_pos = min(round(position)[3] + window, 0),
    Ymin_row = dim(datamat)[2] + Ymin_pos + 1,
    Ymax_row = dim(datamat)[2] + Ymax_pos - 1
  )

  # Height of the block (min - 1/5 of total height) to correct z
  # soliddepth <- min(datamat, na.rm = TRUE))/zscale)
  one_5 <- (max(datamat, na.rm = TRUE) - min(datamat, na.rm = TRUE))/5
  soliddepth <- (min(datamat, na.rm = TRUE) - one_5)/zscale
  
  # Calculate new position of the point on the cropped raster
  position_bounds <- position %>% 
    mutate(
      X_ray = X_ray - bounds$Xmin + 1,
      Y_2d = Y_ray - bounds$Ymin_pos + 1,
      Y_ray = -1 * (Y_ray - bounds$Ymin_pos + 1),
      Z_ray = Z_ray #/zscale
    )

  # Plot cropped 3D output
  ray_image[bounds$Ymin_row:bounds$Ymax_row,bounds$Xmin:bounds$Xmax,] %>% 
    plot_3d(
      datamat[bounds$Xmin:bounds$Xmax, bounds$Ymin_row:bounds$Ymax_row],
      zscale = zscale, windowsize = windowsize,
      # soliddepth = -min(datamat, na.rm = TRUE)/zscale,
      soliddepth = soliddepth,
      water = TRUE, wateralpha = 0,
      theta = -90, phi = 30, 
      zoom = zoom, 
      fov = 80)
  
  # Add point at position
  spheres3d(position_bounds[,c("X_ray", "Z_ray", "Y_ray")],
            color = "red", add = TRUE, lwd = 5, radius = 5,
            alpha = 1)

  if (!missing(position_next)) {
    position_next_bounds <- position_next %>% 
      mutate(
        X_ray = X_ray - bounds$Xmin + 1,
        Y_2d = Y_ray - bounds$Ymin_pos + 1,
        Y_ray = -1 * (Y_ray - bounds$Ymin_pos + 1),
        Z_ray = Z_ray
      )
    
    # Add point at position
    spheres3d(position_next_bounds[,c("X_ray", "Z_ray", "Y_ray")],
              color = "blue", add = TRUE, lwd = 5, radius = 3,
              alpha = 1)
  }
}

path_gif <- file.path(extraWD, "film_follow_trajectory.gif")
if (!file.exists(path_gif)) {
  
  # Number of frame = Number of points
  n_frames <- length(poudre_rays$coords$coords)
  savedir <- file.path(extraWD, "film_follow_trajectory")
  if (!dir.exists(savedir)) {
    dir.create(savedir, showWarnings = FALSE)
  }
  img_frames <- file.path(
    savedir,
    paste0("film_", formatC(seq_len(n_frames), width = 3, flag = "0"), ".png")
  )
  
  # create all frames
  for (i in seq_len(n_frames)) {
    # i <- 20
    position <- poudre_rays$coords$coords[[i]]
    if (i < n_frames) {
      position_next <- poudre_rays$coords$coords[[i + 1]]
      render_cropped_scene(ray_image, datamat, position,
                           position_next)
    } else {
      # Last one
      render_cropped_scene(ray_image, datamat, position)
    }
    # Save img
    rgl::snapshot3d(img_frames[i])
    rgl::clear3d()
  }
  rgl::rgl.close()
  
  # Create gif
  magick::image_write_gif(magick::image_read(img_frames), 
                          path = path_gif, 
                          delay = 6/n_frames)
}
```

